% rrii_scroll_qr_dynamic.tex — $\phi^0$ ↔ .rii Scroll ↔ QR ↔ PDF Reconstruction Engine
% Author: Ni1K / Cosmic Precision Layer
% Validated on: \today

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,geometry,xcolor}
\geometry{margin=1in}

% Theorem Environments
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{proposition}[definition]{Proposition}

\title{$\phi^0$ \(\leftrightarrow\) .rii Scroll \(\leftrightarrow\) QR Code \(\leftrightarrow\) Harmonic Memory Field}
\author{Declared by Ni1K \quad| \quad Cosmic Precision Layer}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present a deterministic, invertible engine linking a canonical $\phi$‑scroll PDF (`.rii`) through QR‑seeded phases to dynamically reconstructed PDF pages at any $\phi$‑level.  This “$\phi$‑Scroll \(\leftrightarrow\) QR \(\leftrightarrow\) PDF” pipeline supports:
\begin{itemize}
  \item Ancestral compression ($\phi^{-n}$),
  \item Canonical recall ($\phi^0$),
  \item Speculative bloom ($\phi^{+n}$),
  \item Visual bubbles, QR textures, memory glyph overlays,
  \item \textbf{Petal 29:} A full tree of 26 documented RII$^\pm$ pairs with formal derivations, visualization specs, and Rood + Alpha\_FISH scaling.
\end{itemize}
Appendix A contains first‑principles derivations.
\end{abstract}

\setcounter{tocdepth}{1}
\tableofcontents

\newpage

\section{$\phi^6$: The Heart of Dimensional Recursion}
\label{sec:phi6}

\subsection*{Insight}
At $\phi^6\approx17.944$, spiral recursion transcends mere scaling to effect true dimensional cross‑connection: radial expansion meets angular recursion, Möbius flips occur, and dual spirals reflect across a sacred hinge.

\subsection*{Definition}
\[
\phi^6 = \Bigl(\tfrac{1+\sqrt5}{2}\Bigr)^6.
\]

\subsection*{Key Properties}
For spiral states $S_n=\phi^n$ and $S_m=\phi^m$ with $n+m=6$:
\begin{itemize}
  \item \textbf{Symmetry:} $\phi^6$ is the harmonic midpoint between $\phi^3$ and $\phi^9$.
  \item \textbf{Dual Mirroring:} iPEARLs at $n=3$ reflect across $\phi^6$.
  \item \textbf{Resonance:} Phase‑locked recursion nodes align at $\phi^6$.
  \item \textbf{Toroidal Flip:} Möbius reflection where twist meets recursion.
\end{itemize}

\subsection*{Dimensional Interpretation}
The product $S_n\cdot S_m=\phi^{n+m}$, for $n+m=6$, yields a geometric fold carrying:
\[
\bigl(\text{spatial charge},\;\text{temporal offset},\;\text{memory anchor}\bigr).
\]

\subsection*{Petal Implications}
$\phi^6$ acts as a \emph{mirrorline}:
\[
\phi^k \longleftrightarrow \phi^{6-k},\quad k=1,\dots,5,
\]
with $\phi^6$ itself the central axis.

\section{Core Definitions}

\begin{definition}[$\phi$‑Scroll Snapshot]
$\mathcal{S}_0$: The canonical `.rii.pdf` at $\phi^0$, containing the full scroll of glyphs and geometry.
\end{definition}

\begin{definition}[QR Seed Glyph]
A tuple $Q=(\mathrm{sigil},\,n,\,\mathbf{q},\,b)$ with
\[
\mathrm{sigil}\in\texttt{String},\quad
n\in\mathbb{Z},\quad
\mathbf{q}\in\mathbb{R}^3,\;\|\mathbf{q}\|=1,\quad
b\in[0,1].
\]
\end{definition}

\begin{definition}[PDF Binding Operator]
\[
P_{\phi}: Q \;\longmapsto\; \mathcal{S}_{\phi},
\]
where $\mathcal{S}_{\phi}$ is the PDF–derived page set at dilation level $\phi^n$.
\end{definition}

\section{QR‑to‑PDF Binding}

\begin{proposition}[Binding at $\phi^0$]
\[
P_0(Q)\;=\;\mathcal{S}_0,
\]
the original scroll. For $n\neq0$, $P_n(Q)$ transforms $\mathcal{S}_0$ via bubble overlays and glyph blooms.
\end{proposition}

\begin{definition}[Phase‑Indexed Binding]
For $n\in\mathbb{Z}$,
\[
P_n(Q)
=\operatorname{RenderPDF}\bigl(\mathcal{S}_0;\,n,Q\bigr),
\]
where \texttt{RenderPDF} applies:
\begin{itemize}
  \item Compression $\mathcal{C}_{-n}$ if $n<0$,
  \item Expansion $\mathcal{E}_{+n}$ if $n>0$,
  \item Bubble overlay field $\mathcal{B}(Q,n)$.
\end{itemize}
\end{definition}

\section{QR Field as Page Generator}

\begin{definition}[Bubble Packet]
\[
\mathcal{B}(Q,n)
=\{\,b_i(\phi^n)\}_{i=1}^N,
\quad
b_i=(x_i,y_i,r_i,\alpha_i,C_i,g_i),
\]
denoting position, radius, opacity, color, and glyph content.
\end{definition}

\begin{definition}[Page Assembly]
\[
\mathcal{S}_n
=\bigcup_{i=1}^N b_i(\phi^n)\;\cup\;\mathcal{S}_0,
\]
layered (background scroll + bubbles).
\end{definition}

\section{Dynamic PDF Assembly Engine}

\begin{definition}[Assembly Engine]
\[
\mathcal{A}:(\mathcal{S}_0,Q,n)\;\longmapsto\;\mathrm{PDF}(\mathcal{S}_n),
\]
where $\mathcal{A}$:
\begin{enumerate}
  \item Computes $\mathcal{B}(Q,n)$.
  \item Renders each $b_i$ as an SVG overlay.
  \item Merges overlays atop $\mathcal{S}_0$ via a PDF library.
  \item Embeds metadata $\langle Q,n,\mathrm{timestamp}\rangle$.
\end{enumerate}
\end{definition}

\section{Validation}

\begin{enumerate}
  \item \textbf{Invertibility:} 
    $\mathcal{C}_{-n}(\mathcal{E}_n(\mathcal{S}_0))=\mathcal{S}_0$.
  \item \textbf{Determinism:} 
    Identical inputs yield bit‑identical PDFs.
  \item \textbf{Phase Continuity:} 
    The sequence $\{P_n(Q)\}$ is smooth in $n$.
  \item \textbf{Archival‑Grade:} 
    Each PDF embeds SHA‑256$(Q,n)$ and scroll hash.
\end{enumerate}

\section{Example Workflow}

\begin{enumerate}
  \item Generate $Q_0$ at $\phi^0$.
  \item Invoke $\mathcal{A}(\mathcal{S}_0,Q_0,0)\to P_0(Q_0)$.
  \item For $n\in\{-29,-15,0,+15,+29\}$ compute $P_n(Q_0)$.
  \item Collate pages:
    \[
      [P_{-29},\,P_{-15},\,P_0,\,P_{+15},\,P_{+29}].
    \]
\end{enumerate}

\section{Petal 29: RII$^\pm$ Pair Tree}

A binary tree of 26 RII$^+$ and RII$^-$ pairs, each node containing:
\begin{itemize}
  \item Formal derivation,
  \item Visualization spec,
  \item Rood + Alpha\_FISH scaling.
\end{itemize}

\appendix
\section{Appendix A: First‑Principles Derivations}
Detailed proofs of $\phi^6$ symmetry, bubble geometry, and invertibility.

\end{document}
